Supplementary Material for the Paper ``Enriching Object Detection with\\2D-3D Registration and Continuous Viewpoint Estimation''

### 2014-11-20 egpaper_supp.tex
done pass over supp

  \caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a

@@

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
  \hline
  \end{tabular}
\caption{Successful detection and pose estimation result on PASCAL3D+ dataset
  bicycle category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
  car category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on PASCAL3D+ dataset
  bicycle category, On each column, original image is on the left and overlaid
  2D-3D registration on the right with a proposal bounding box (blue) and a
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_bad}
\end{figure*}

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{From left to right, original images, initial pose estimations and
fine-tuned result. The numbers, from the left, indicate detection confidence
and intersection over union respectively.} 
  \label{fig:tuning}
\end{figure*}

>>>>

  \caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and

@@

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle13b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle6b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle7b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle8b.png}  \\
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9a.png} &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle9b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle10b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle2b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle12b.png}  \\
  \hline
  \end{tabular}
\caption{Successful detection and pose estimation results on
    PASCAL3D+~\cite{Xiang14} bicycles. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_good}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car2b.png} & 
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4a.png} &
%   \includegraphics[width=0.24\linewidth]{supp/pas_car4b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car8a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car8b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car9a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car9b.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car11a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car11b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car12a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car12b.png} \\
  \includegraphics[width=0.22\linewidth]{supp/pas_car14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car14b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_car15a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car15.png} \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_car20a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car20b.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_car23b.png} \\
  \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on
  PASCAL3D+~\cite{Xiang14} cars. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).} 
  \label{fig:pascal3d_car_bad}
\end{figure*}

\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{|cc|cc|}
  \hline
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle14b.png} & 
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15a.png}  &
  \includegraphics[width=0.15\linewidth]{supp/pas_bicycle15b.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle16b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle17b.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18a.png} &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle18b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19a.png}  &
  \includegraphics[width=0.22\linewidth]{supp/pas_bicycle19b.png}  \\   \hline
  \end{tabular}
\caption{Failed detection or pose estimation result on
  PASCAL3D+~\cite{Xiang14} bicycles. Original image (left) and
  overlaid detection result (right). Proposal bounding box (blue) and
  predicted bounding box (purple).} 
  \label{fig:pascal3d_bicycle_bad}
\end{figure*}

\section{Fine Tuning}
Lastly, we provide qualitative examples of the fine-tuning stage of
our pipeline based on MCMC sampling (Sect.~5 in the main paper) in
Fig.~\ref{fig:tuning}. Please note that, while the visual difference
appear subtle, our method often manages to improve upon the initial
pose estimate.
%
\begin{figure*}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{ccc}
  \includegraphics[width=0.22\linewidth]{supp/tuning_1a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_1b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_1c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_2a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_2b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_2c.png}  \\ 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_3b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_3c.png}  \\   
  \includegraphics[width=0.22\linewidth]{supp/tuning_4a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_4b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_4c.png}  \\     
  \includegraphics[width=0.22\linewidth]{supp/tuning_5a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_5b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_5c.png}  \\
  \includegraphics[width=0.22\linewidth]{supp/tuning_6a.png} &
  \includegraphics[width=0.22\linewidth]{supp/tuning_6b.png} & 
  \includegraphics[width=0.22\linewidth]{supp/tuning_6c.png}  \\
  \end{tabular}
\caption{Effect of fine-tuning based on MCMC sampling. From left to
  right: original image, initial pose estimate, and fine-tuned
  result. Numbers indicate detection confidence (s) and intersection
  over union (o), respectively.} 
  \label{fig:tuning}
\end{figure*}
